\documentclass{article}
\usepackage[utf8]{inputenc}
\title{HW0-report.pdf}
\author{Shuolun Chang }
\date{January 2020}

\begin{document}

\maketitle
Q1. Explore the class website. Where can you find lecture topics and assignments?\\

A1.Open the class website and click the "this week" under the "Schedule", than the assignment topic and due date will be displayed. Then click "HW(n)" to jump to the GitHub classroom interface, where the assignment would be posted.\\

Q2. Make a posting using the hw0 tag in our class Piazza group. The posting should just be a brief introduction of yourself to the rest of the class. Copy the text of your posting into your report.\\

A2.HW0 Introduction: 
Hi everyone, my name is Alan Chang and I'm new to ODU. This is my first semester and I'm interested in this Web Science subject. I wish I can learn some knowledge about this topic and put it in practice. \\



Q3. Answer the following questions:

a) What is your GitHub username?\\


A3.a) My GitHub username is AlanChang001\\

b) Accept the GitHub Classroom invitation for HW0. What is the URL of the generated repo?\\

A3.b) The URL of the generated repo is: https://github.com/cs432-websci-spr20/hw0-setup-AlanChang001\\


Q5. Copy the LaTeX source for your solution to Typesetting Exercise 1 (slide 11) from part 1 of the intro into your report. Download the generated PDF from Overleaf. If you are using Markdown, push the generated PDF to your repo and include a link to it in your report. If you are using LaTeX for your report, include the PDF as an image in your report.
\\

Q6. Read the Web Services page and create a basic HTML page. (You can copy the code from this simple HTML page or do something more elaborate.) Put the URL to your webpage in your report. (Make sure that the link works.)\\

A6. I requested an odu account and read all the instruction. I tried to connect the odu linux server with my own laptop but failed.  
Q7. Pick one of the simple examples from Python examples and execute it. Take a screenshot of the terminal and include as a figure in your report.\\

A7. I uploaded my screenshot of the python example result. Please see the attachment.\\


Q8. Section 3.2 shows a scatterplot of hwy vs. displ using the mpg data. Create a scatterplot of hwy vs. cyl. Include the R code used to generate the chart and a PNG version of the chart in your report.\\

A8. I uploaded my screenshot of the scatterplot generated by the R-Studio. Please see the attachment
\end{document}
